### 2025-04-18 multiple-regression.qmd
20250417 - figures

```{r}
#| layout-ncol: 2
#| label: fig-distributionQQplots
#| fig-cap: "Quantile–Quantile (QQ) Plots of Various Distributions."
#| fig-alt: "Quantile–Quantile (QQ) Plots of Various Distributions."
#| fig-subcap:
#|   - "Normal Distribution"
#|   - "Normal Distribution"
#|   - "Bimodal Distribution"
#|   - "Bimodal Distribution"
#|   - "Negatively Skewed Distribution"
#|   - "Negatively Skewed Distribution"
#|   - "Positively Skewed Distribution"
#|   - "Positively Skewed Distribution"
#|   - "Platykurtic (Light-Tailed) Distribution"
#|   - "Platykurtic (Light-Tailed) Distribution"
#|   - "Leptokurtic (Heavy-Tailed) Distribution"
#|   - "Leptokurtic (Heavy-Tailed) Distribution"
#| code-fold: true

@@

car::qqPlot(
  distribution_normal,
  main = "QQ Plot",
  id = TRUE)

@@

car::qqPlot(
  distribution_bimodal,
  main = "QQ Plot",
  id = TRUE)

@@

car::qqPlot(
  distribution_negativeSkew,
  main = "QQ Plot",
  id = TRUE)

@@

car::qqPlot(
  distribution_positiveSkew,
  main = "QQ Plot",
  id = TRUE)

@@

car::qqPlot(
  distribution_lightTailed,
  main = "QQ Plot",
  id = TRUE)

@@

car::qqPlot(
  distribution_heavyTailed,
  main = "QQ Plot",
  id = TRUE)
```

>>>>

```{r}
#| layout-ncol: 2
#| label: fig-distributionQQplots
#| fig-cap: "Quantile–Quantile (QQ) Plots of Various Distributions (Right Side) with the Histogram of the Associated Distribution (Left Side)."
#| fig-alt: "Quantile–Quantile (QQ) Plots of Various Distributions (Right Side) with the Histogram of the Associated Distribution (Left Side)."
#| fig-subcap:
#|   - "Normal Distribution"
#|   - "Normal Distribution"
#|   - "Bimodal Distribution"
#|   - "Bimodal Distribution"
#|   - "Negatively Skewed Distribution"
#|   - "Negatively Skewed Distribution"
#|   - "Positively Skewed Distribution"
#|   - "Positively Skewed Distribution"
#|   - "Platykurtic (Light-Tailed) Distribution"
#|   - "Platykurtic (Light-Tailed) Distribution"
#|   - "Leptokurtic (Heavy-Tailed) Distribution"
#|   - "Leptokurtic (Heavy-Tailed) Distribution"
#| code-fold: true

@@

car::qqPlot(
  distribution_normal,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_bimodal,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_negativeSkew,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_positiveSkew,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_lightTailed,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_heavyTailed,
  main = "QQ Plot")
```
